---
title: "tidy-model"
author: "ebonylz"
date: "2025-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse') ; library('modeldata')
```

## Introduction

This R markdown document demonstrates my abilities to use models for data analysis using a data set collected on crickets


```{r load data, include = FALSE}
data(crickets, package = "modeldata")
names(crickets)
```

## What is that sound?
In this report, we examine what factors predict a cricket's chirp rate

```{r summary, echo = FALSE}
summary(crickets)
ggplot(crickets, aes(x = rate)) +
  geom_histogram(bins = 8) +
  ggtitle("Distribution of the chirp rate of crickets") +
  xlab('Chirp rate (per min.)')
```

## Temperature affects chirp rate

According to this scatter plot of temperature vs chirping rate, as temperature increases as does chirping

```{r temp, echo = FALSE}
ggplot(crickets, aes(x=temp, y=rate)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  ggtitle("Plot of temperature and chirp rate") +
  ylab('Chirp rate (per min.)') +
  xlab('Temperature (Celsius)')
```

