---
title: "tidy-model-diamonds"
author: "ebonylz"
date: "2025-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse') ; library('modeldata')
```

## Introduction

This R markdown document demonstrates my abilities to use models for data analysis using a data set collected on diamonds

```{r load data, include = FALSE}
data(ggplot2::diamonds, package = "modeldata")
names(diamonds)
```

## Introduction

3 variables I will be using is price, carat, and cut of a diamond to predict price of diamonds

```{r histogram, echo = FALSE}
summary(diamonds)
ggplot(diamonds, aes(x = price, fill=cut)) +
  geom_histogram() +
  ggtitle("Distribution of Price and cut of Diamonds") +
  xlab('Price of diamond')
```

## How does the carat of a diamond affect the price?

According to this plot, on average a 1-unit increase in carat increases the price by $7,756.43. The error in this report is ($1549) meaning that the model is good but not perfect This model explains 84.93% of the variation based on carat alone

```{r price carat, echo = FALSE}
ggplot(diamonds, aes(x=carat, y=price)) +
  geom_point(alpha = 0.5) + 
  geom_smooth(method = 'lm', se = FALSE) +
  ggtitle("Plot of Price vs Carat of Diamonds") +
  ylab('Price of Diamond') +
  xlab('Carat') +
  theme_minimal()

price_lm <- lm(lm(price ~ carat, data = diamonds))

summary(price_lm)
```

## how does the cut and carat of a diamond change the price of a diamond?

In this plot, it shows that higher quality cut does increase the price by about $1239.80 per step of cut. The standard error is $1511 and 85.65% variance in price which is an improvement from the previous plot, but can still use room for improvement

```{r price carat cut, echo = FALSE}
ggplot(diamonds, aes(x=carat, y=price, color=cut)) +
  geom_point(alpha = 0.3) + 
  geom_smooth(method = 'lm', se = FALSE) +
  ggtitle("Plot of Price vs Carat of Diamonds") +
  ylab('Price of Diamond') +
  xlab('Carat') +
  theme_minimal()

price_lm <- lm(price ~ carat + cut, data = diamonds)

summary(price_lm)
```
